State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2014-11-28 paper/chapters/3_preprocessing.tex
backup

\subsection{Tokenizer}
There are already free tokenizer implementations
 available. Some popular programming 
libraries for the english language include the Stanford 
NLP PTBTokenizer\footnote{http://nlp.stanford.edu/software/tokenizer.shtml} 
and the Apache OpenNLP Tokenizer\footnote{http://opennlp.apache.org/documentation/manual/opennlp.html}.
These examples are quite versatile and can be even 
used for different tasks and languages. Another 
example is the specialized Carnegie Mellon Twokenizer\footnote{http://www.ark.cs.cmu.edu/TweetNLP/},
which is especially for the tokenization of tweets.

@@

%Besondere an twitter: Hashtags, Mentions, Smileys
Some words are difficult to handle. One example are emoticons,
because they are hard to recognize correctly. Although they 
are a good and popular ressource for sentiment analysis.

>>>>

\subsection{Tokenizer}
There are already several open source tokenizer implementations
available. Some popular programming libraries for the english 
language include the Stanford NLP PTBTokenizer
\footnote{http://nlp.stanford.edu/software/tokenizer.shtml} 
and the Apache OpenNLP Tokenizer\footnote{http://opennlp.apache.org/documentation/manual/opennlp.html}.
These examples are quite versatile and can be even 
used for different tasks and languages.
The restirction of 140 Characters leads to a heavy
usage of slang, emoticons and punctuation 
that are uncommon in longer text messages.\autocite{davies2011}
This circumstances give rise to specialized Tokenizer
for tweets. One example is the specialized Carnegie 
Mellon Twokenizer\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}.

@@

%Besondere an twitter: Hashtags, Mentions, Smileys
Some words are difficult to handle. One example are emoticons,
because they are hard to recognize correctly. Although they 
are a good and popular ressource for sentiment analysis. \autocite{emoticons}
